Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-16 ms.tex
more clean-up of zero-point section

\subsection{Zero-Point}
\label{sec:zp}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
 by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
correlating the other Planck channels against the corrected 857 GHz map. We 
have not altered the \verb|i100| zero-point in any way. We have also removed 
the Solar dipole residual according to \cite{planckdust}, by subtracting a 
dipole pattern oriented toward $(l, b) = ()$ and scaled according to their 
Table 1.

@@

With $i$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the Planck 857 GHz map with zodiacal emission, compact 
sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution Planck 217 GHz 
map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
satisfy the low HI cut, we have an overconstrained linear model with three
parameters: a, b, and c. $a$ represents the slope of Planck 217 GHz 
versus Planck 857 GHz assuming they are linearly correlated, and is not
of any importance to our downstream analysis. $b$ represents the scaling of 
the Solar dipole that makes the 857 GHz vs. 217 GHz correlation tightest, and 
$c$ represents the constant offset necessary to make the zero level of the 217 
GHz map consistent with that of the 857 GHz map. Performing a linear least
squares fit with uniform weights and iterative outlier rejection, we find 
$a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
amplitude, which is within the calibration uncertainty of the 217 GHz band. 
Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation before 
and after correcting for our best-fit offset and dipole residual. Not only is 
the improvement striking in this scatterplot, but the residual dipole also 
appears visually well-corrected in the 217 GHz map itself.

>>>>

\subsection{Zero-Point}
\label{sec:zp}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
 by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
correlating the other \PLANCK~channels against the corrected 857 GHz map. We 
have not altered the \verb|i100| zero-point in any way. We have also removed 
the Solar dipole residual according to \cite{planckdust}, by subtracting a 
dipole pattern oriented toward $(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and 
scaled according to their Table 1.

@@

With $i$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution \PLANCK~217 
GHz map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
satisfy the low HI cut, we have an overconstrained linear model with three
parameters: a, b, and c. $a$ represents the slope of \PLANCK~217 GHz 
versus \PLANCK~857 GHz assuming they are linearly correlated, and is not
of any importance to our downstream analysis. $b$ represents the scaling of 
the Solar dipole that makes the 857 GHz vs. 217 GHz correlation tightest, and 
$c$ represents the constant offset necessary to make the zero level of the 217 
GHz map consistent with that of the 857 GHz map. Performing a linear least
squares fit with uniform weights and iterative outlier rejection, we find 
$a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
amplitude, which is within the calibration uncertainty of the \PLANCK~217 GHz 
band. Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation 
before and after correcting for our best-fit offset and dipole residual. Not 
only is the improvement striking in this scatterplot, but the residual dipole 
also appears visually well-corrected in the 217 GHz map itself. Before 
performing thermal dust fits, we therefore subtract $c$ and $b\mathcal{D}$ from
the 217 GHz map.
